gilmore-nysds-2016

### 2016-08-11 nysds-2016/gilmore-nysds-2016.Rmd
initial NYSDS 16 commit

---
title: "To boldly go where no science..."
author: "Karen E. Adolph, David Millman, and Rick O. Gilmore"
output: 
  ioslides_presentation:
    widescreen: TRUE
    css: css/databrary.css
    logo: img/databrary-leaf-large.png
bibliography: bib/databrary.bib
---

@@

@@

- Video is essential for reproducible behavioral science
    + Even where video is *not* the primary raw data
- [Databrary](http://databrary.org) specializes in storing and sharing research video
- Video is identifiable, but it *can* be shared
- *All* behavioral scientists should collect and share videos of their research

@@

@@

- Video record all tasks, measures, and behaviors
- Share the recordings
- Share all questionnaires, tasks, displays
- Share statistical, computational, data workflows
- Prepare to share from the beginning
- Seek permission to share data

@@

- Digital data library specialized for research video
- Video/audio + participant/context metadata
- Share displays, materials, text-based data files
- Restricted access for research/educational use
- Policy framework for sharing identifiable data
- Developmental focus, but not exclusive

@@

- Policies for sharing identifiable video data
- Tools for reproducibly coding video
- Tools for "active curation" == during data collection

@@

@@

@@

- Video uniquely captures complexity & richness of behavior
- Video captures vital methodological details
- Identifiable video (and other data) can be shared
- Preparing to share reduces the burden
- Video data sharing essential for a reproducible behavioral science

@@

<http://github.com/databrary/presentations/nyu-data-science-reproducibility-16/>
</div>

>>>>

---
title: "gilmore-nysds-2016"
author: "Rick O. Gilmore, Karen E. Adolph, & David S. Millman"
date: "`r Sys.Date()`"
output:
  ioslides_presentation:
    widescreen: TRUE
    css: css/databrary.css
    logo: img/databrary-leaf-large.png
bibliography: bib/databrary.bib
---

@@

**Curating identifiable data**

@@

- Video is essential for reproducible behavioral science
    + Even where video is *not* the primary raw data
- [Databrary](http://databrary.org) specializes in storing and sharing research video
- Video is identifiable, but it *can* be securely stored, managed, and shared
- **All** behavioral scientists should collect and share videos of their research

@@

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/9840/-/asset/11192/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
[[@c7fbeef0-d8a9-4b99-9e17-f598507486b7]](http://doi.org/10.17910/B7H019)
</div>

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/9840/-/asset/11193/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
[[@c7fbeef0-d8a9-4b99-9e17-f598507486b7]](http://doi.org/10.17910/B7H019)
</div>

@@

>- Video record all tasks, measures, and behaviors
>- Share the recordings openly with other researchers
>- Share all questionnaires, tasks, displays
>- Share statistical, computational, data workflows
>- Prepare to share from the beginning
>- Seek permission to share data from participants

@@

- Digital data library specialized for research video
- Video/audio + participant/context metadata
- Share displays, materials, text-based data files

- Restricted access for research/educational use
- Policy framework for sharing identifiable data
- Developmental focus, but not exclusive

- High capacity, centralized storage
- Transcoding to common, interoperable formats
- Long-term preservation

## Databrary's progress

- Support from NSF and NICHD in late 2012, early 2013.
- Website "live" early 2014.
- Rapid growth in investigators, institutions, datasets.

<iframe src="https://databrary.org" width=750px height=500px>
</iframe>

@@

- Policies for sharing identifiable video data
- Tools for reproducibly coding video
- Tools for "active curation" == during data collection
- Tools for searching, filtering

@@

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/223/-/asset/47075/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>
</iframe>

## Video is just a spatially and temporally rich time series

<div class="centered">
<img src="http://www.psyrecon.de/uploads/pics/psychophysiologischeVariablen_01.jpg">
</div>

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/11141/0,5000/asset/37958/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>
</iframe>

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/11141/0,5000/asset/37962/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>
</iframe>

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/11141/0,5000/asset/37968/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>
</iframe>

## Datavyu can import multiple time series

- Heart rate, skin conductance, brain activation
- Eye position, diameter
- Body position, movement

@@

## Common metadata representation makes search, filtering easy

<div class="centered">
<img src="img/search=1-2-y-olds.jpg">
**"Show me all the datasets that have videos of 1-2 year-old children"**
</div>

@@

- Video uniquely captures complexity & richness of behavior
- Video captures vital methodological details
- Identifiable video (and other data) can be shared securely and ethically
- Preparing to share reduces the burden
- Video data sharing essential for a reproducible behavioral science

@@

<http://github.com/databrary/presentations/nysds-2016/>
</div>
